A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-09 docs/methods/erosion_methods.tex
NM

\bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
J.~M. Huang, M.N.J. Moore, and L.~Ristroph.
\newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
\newblock \emph{Journal of Fluid Mechanics}, 765, 2 2015.
\newblock ISSN 1469-7645.

@@

\bibitem[Moore(2017)]{moore2017riemann}
M~Nicholas~J Moore.
\newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
  Melting, and Eroding in Fluid Flows}.
\newblock \emph{Communications on Pure and Applied Mathematics}, 70\penalty0
  (9):\penalty0 1810--1831, 2017.

\bibitem[Moore et~al.(2013)Moore, Ristroph, Childress, Zhang, and
  Shelley]{moo-ris-chi-zha-she2013}
Matthew N.~J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
  Michael~J. Shelley.
\newblock Self-similar evolution of a body eroding in a fluid flow.
\newblock \emph{Physics of Fluids}, 25:\penalty0 116602, 2013.

>>>>

\bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
J.M. Huang, M.N.J. Moore, and L.~Ristroph.
\newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
\newblock \emph{Journal of Fluid Mechanics}, 765, 2 2015.
\newblock ISSN 1469-7645.

@@

\bibitem[Moore(2017)]{moore2017riemann}
M.N.J. Moore.
\newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
  Melting, and Eroding in Fluid Flows}.
\newblock \emph{Communications on Pure and Applied Mathematics}, 70\penalty0
  (9):\penalty0 1810--1831, 2017.

\bibitem[Moore et~al.(2013)Moore, Ristroph, Childress, Zhang, and
  Shelley]{moo-ris-chi-zha-she2013}
Matthew N.J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
  Michael~J. Shelley.
\newblock Self-similar evolution of a body eroding in a fluid flow.
\newblock \emph{Physics of Fluids}, 25:\penalty0 116602, 2013.
